A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-04-18 ASOC/paper.Rnw
Starting version for Applied and Soft Computing

\documentclass[runningheads,a4paper]{llncs}

\usepackage[latin1]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{url}
\usepackage{caption}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

@@

\author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
  Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain \and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

@@

%\thispagestyle{empty}
%\pagestyle{empty}

@@

\bibliographystyle{splncs}
\bibliography{volunteer,GA-general,geneura,javascript,ror-js}

>>>>

\documentclass[preprint]{elsarticle}
\biboptions{longnamesfirst,angle,semicolon}

\journal{Applied and Soft Computing}

\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage{url}
\usepackage{caption}

@@

\author[jjmg]{Juan-J.~Merelo\corref{cor1}\fnref{fn1}}
\ead{jmerelo@ugr.es}

\author[pcd]{Paloma de las Cuevas \fnref{fn1}}
\ead{palomacd@ugr.es}

\author{Pablo Garc\'ia-S\'anchez\fnref{fn1}}
\ead{fergunet@gmail.com}

\author{Mario Garc\'ia-Valdez \fnref{fn2}}
\ead{mario@tectijuana.edu.mx}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{Dept. of Computer Architecture and Technology and CITIC, University
of Granada, Spain}
\fntext[fn2]{Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

\begin{keyword}

  Volunteer computing, pool-based evolutionary algorithms
\end{keyword}

@@

@@

\section*{References}

\bibliographystyle{elsarticle-num}
\bibliography{volunteer,GA-general,geneura,javascript,ror-js}
